Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-07-23 pirouette_article.tex
Show parameters explictly, as suggested by @rsetienne

\new{
	To allow users to extend the functionalities of BEAST
	using plug-ins, BEAST2 was written [\cite{bouckaert2019beast}]
	(with BEAST and BEAST2 still independently being developed further).
	For example, one can add novel diversification models 
	by writing a BEAST2 plugin that contains 
	the likelihood formula of a phylogeny under the novel diversification model, 
	i.e. the prior probability of a species tree.
	Plugins have been provided, for instance, for the calibrated 
	Yule model [\cite{heled2015calibrated}],
	  the BD model with incomplete sampling [\cite{stadler2009incomplete}],
	  the BD moel with serial sampling [\cite{stadler2012estimating}],
	  the BD serial skyline model [\cite{stadler2013birth}],
	  the fossilized BD process [\cite{gavryushkina2014bayesian}], and
	  the BD SIR model [\cite{kuhnert2014simultaneous}].
}

@@

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/errors.png}
  \caption{
    \new{The inference error made 
    when using the generative substitution and clock models (in this case JC69 and strict clock) and a Yule tree prior (this is the assumed generative model because the real generative model is of course unknown) and when using the best-fitting candidate model (in this case JC69, relaxed lognormal and BD), for both the true tree generated by the novel diversification model and for the twin tree.
    The twin distributions show the baseline inference error.}
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_30}
\end{figure}

>>>>

\new{
	To allow users to extend the functionalities of BEAST
	using plug-ins, BEAST2 was written [\cite{bouckaert2019beast}]
	(with BEAST and BEAST2 still independently being developed further).
	For example, one can add novel diversification models 
	by writing a BEAST2 plugin that contains 
	the likelihood formula of a phylogeny under the novel diversification model, 
	i.e. the prior probability of a species tree.
	Plugins have been provided, for instance, for the calibrated 
	Yule model [\cite{heled2015calibrated}],
	  the BD model with incomplete sampling [\cite{stadler2009incomplete}],
	  the BD model with serial sampling [\cite{stadler2012estimating}],
	  the BD serial skyline model [\cite{stadler2013birth}],
	  the fossilized BD process [\cite{gavryushkina2014bayesian}], and
	  the BD SIR model [\cite{kuhnert2014simultaneous}].
}

@@

# Create the inference model for the generative model explicitly
pir_params$experiments[[1]]$inference_model$tree_prior <- create_yule_tree_prior()
pir_params$experiments[[1]]$inference_model$site_model <- create_jc69_site_model()
pir_params$experiments[[1]]$inference_model$clock_model <- create_strict_clock_model()

# Simulate a twin tree using BD explicitly
pir_params$twinning_params$sim_twin_tree_fun <- get_sim_bd_twin_tree_fun()

@@

\begin{figure}[H]
  \includegraphics[width=\textwidth]{pirouette_example_30/errors.png}
  \caption{
    \new{The inference error made 
    when using the generative substitution and clock models (in this case JC69 and strict clock) and a Yule tree prior (this is the assumed generative model because the real generative model is of course unknown) and when using the best-fitting candidate model (in this case JC69, relaxed log-normal and BD), for both the true tree generated by the novel diversification model and for the twin tree.
    The twin distributions show the baseline inference error.}
    Vertical dashed lines show the median error value per distribution.
  }
  \label{fig:example_30}
\end{figure}
